# File converter

The script `1.Pipeline_extension_format_converter.R` is available under the folder of `J:\CBMR\SUN-CBMR-Metabolomics\Workflow\Script\modules` 



## Source paths on the server
```{r eval=FALSE}
source("H:/From_SUND/Scripts/utils/utils_MS2_set_up/set_up_paths.R")
```



## Specify the polarity 🕵
```{r eval=FALSE}
polarity <- "POS" #other options "NEG", "c("POS", "NEG")"
```

  

## Path of application of openms 🕵
```{r eval=FALSE}
path_openms <- "C:/Program Files/OpenMS-2.8.0/bin"
```

  
    
    
## Path of storing files (.mzML) exported from dataanalysis for each polarity 🕵
```{r eval=FALSE}
path_files_from_DA <- "H:/From_SUND/Scripts/test/MS2pos_untarget"
```

    
    




## Conduct
### Add extension (**if not available**) to files exported from dataanalysis
```{r eval=FALSE}
files_from_DA <- list.files(path_files_from_DA, full.names = TRUE)
id_not_ext <- setdiff(1:length(files_from_DA), 
                      grep("\\.mzML$|\\.d$", basename(files_from_DA)))


if (length(id_not_ext) != 0) {
  

  file.rename(files_from_DA[id_not_ext],
              paste0(files_from_DA[id_not_ext], ".mzML")
             )
}
    
```

    
    
    
### File converter for adapting to run XCMS
```{r eval=FALSE}
source(paste0(path_func, "/file-conversion.R"))

#Create a sibling folder for storing files from openms
path_files_from_openms <- paste0(dirname(path_files_from_DA), "/mzML_openms_MS2_", polarity)
if (!dir.exists(file.path(path_files_from_openms))) dir.create(path_files_from_openms, showWarnings = FALSE, recursive = TRUE)

#conduct converting  
mapply(function(x, y) file_conversion(x,y, path_openms, ".mzML", ".mzML"), path_files_from_openms, path_files_from_DA)
```

    
    
