# MS2 preprocessing targeted
Please copy the template of excel file which fits your data `LCMS_library_template1.xlsx` or `LCMS_library_template2.xlsx` under the folder `J:\CBMR\SUN-CBMR-Metabolomics\Workflow\utils\utils_MS2_preprocessing\LCMS_library_template.xlsx` and fill in the information related to the standards which you would like to preprocess. You must fill the columns with the column name in red color. Regarding the filled filenames, they are without extension




## XCMS_check retention time
Check if the retention time of each standard from MS2 is similar to that from MS1

The script `2b.Pipeline_XCMS_checkRT.R` is available under the folder of `J:\CBMR\SUN-CBMR-Metabolomics\Workflow\Script\modules\MS2_preprocessing`



### Source paths on the server
```{r eval=FALSE}
source("H:/From_SUND/Scripts/utils/utils_MS2_set_up/set_up_paths.R")
```


### Provide polarity 🕵
```{r eval=FALSE}
polarity <- "POS"
```

   
   
### Path of storing .mzML files without filenames 🕵
```{r eval=FALSE}
path_files_mzML <- "H:/From_SUND/Scripts/test/MS2pos_target/mzML_openms_MS2_POS"
```
   
  

### Path of storing outputs 🕵
```{r eval=FALSE}
path_outputs <- "H:/From_SUND/Scripts/outputs"
```



### Filename for containing information of standards including absolute path (Please fill in the provided template) as well as indicating "T1" or "T2" 🕵

- If each sample includes all the same standards, sheet **T1** is suggested to filled in (at least the red names of columns) and put all filenames in the sheet **T1_Filenames**.

- If each sample includes different standards, sheet **T2** is suggested to filled in (at least the red names of columns)

```{r eval=FALSE}
xlsx_std_info <- "H:/From_SUND/Projects/MP163/0220/INFO/LCMS_library_template.xlsx"
xlsx_std_sheetname <- "compound_table"
```
   
   
   
### Colname of retention time 🕵
```{r eval=FALSE}
colname_rt <- "Library.rt.RF" # or "Library.rt.HILLIC"
```

    

   
   
### Threshold for retention time (minutes) and m/z for ploting chromatogram 🕵
```{r eval=FALSE}
thre_rt = 2
thre_mz = 0.01

```



#### Conducting 
```{r eval=FALSE}
source(paste0(path_utils_prepro, "/XCMS_checkRT.R"))
```

   
   
  




## Extraction of MS2-spectra
<font color = "red">If you skip the previous step, please make sure the retention time to be as correct as possible and fill in information related to the standards in the excel file as mentioned in the previous step</font>

The script `3b.Pipeline_extract_MS2_std.R` is available under the folder of `J:\CBMR\SUN-CBMR-Metabolomics\Workflow\Script\modules\MS2_preprocessing`




### Source paths on the server
```{r eval=FALSE}
source("H:/From_SUND/Scripts/utils/utils_MS2_set_up/set_up_paths.R")
```

 
 
 

### Provide polarity 🕵
```{r eval=FALSE}
polarity <- "NEG"
```
   
   
   
### Path of storing .mzML files without filenames 🕵
```{r eval=FALSE}
path_files_mzML <- "H:/From_SUND/Projects/MP163/0220/NEG/mzML_DA_NEG/mzML_openms_MS2_NEG"
```

  

### Path of storing outputs 🕵
```{r eval=FALSE}
path_outputs <- "H:/From_SUND/Projects/MP163/0220/outputs"
```

   

### Absolute path of template with essential information of standards 🕵
```{r eval=FALSE}
xlsx_std_info <- "H:/From_SUND/Projects/MP163/0220/outputs_NEG/metadata_for_MS2.xlsx"
```

  
   
### colname of retention time 🕵
```{r eval=FALSE}
colname_rt <- "rt_detected" # or "Library.rt.RF" # or "Library.rt.HILLIC" 
```


   
### Parameters for extracting MS2 spectra 🕵
#### Extraction: Threshold of rt and m/z for extraction 🕵
```{r eval=FALSE}
params <- list()
params$expandRt <- 5 #seconds
params$expandMz <- 0.01
```

   
   
#### How many maximal number of scans you would like to keep for further getting combined spectrum for each std 🕵
```{r eval=FALSE}
n_scans <- 6 # (5 CEs * 6/ 1 CE * 3)
```
  
   
   
#### Combining: Threshold of mz, proportion among all samples, type for combining, function for combining mz and intensity 🕵
```{r eval=FALSE}
#To get consensus spectra for each feature at each collision energy
params$tolerance <- 0.005
params$peaks <- "intersect"  #"union" #report all peaks from all input spectra 
params$minProp <- 0.7
params$intfun <- max
params$mzfun <- median
```



### Conducting 
```{r eval=FALSE}
if (grepl("ku_00007", path_files_mzML)) {
     
     source("")
     
} else {source(paste0(path_utils_prepro, "/extract_MS2_std.R"))}
```

   
   
  
   



