# MS2 preprocessing untargeted
## XCMS
   The script `2a.Pipeline_XCMS.R` is available under the folder of `J:\CBMR\SUN-CBMR-Metabolomics\Workflow\Script\modules\MS2_preprocessing`




### Source paths on the server
```{r eval=FALSE}
source("H:/From_SUND/Scripts/utils/utils_MS2_set_up/set_up_paths.R")
```



### Provide polarity ðŸ•µ
```{r eval=FALSE}
polarity <- "POS"
```

   
   
   
### Path of storing .mzML files (must have transferred by OpenMS) ðŸ•µ 
```{r eval=FALSE}
path_files_mzML <- "H:/From_SUND/Scripts/test/mzML_openms_MS2_POS"
```

   
  

### Path of storing outputs ðŸ•µ
```{r eval=FALSE}
path_outputs <- "H:/From_SUND/Scripts/outputs"
```

   
   
   
### Parameters for preprocessing ðŸ•µ
#### Filter the compounds eluted too early and too late ðŸ•µ
```{r eval=FALSE}
rt_range <- c(0.5, 15)*60 
```

   
   
#### Peak picking ðŸ•µ
```{r eval=FALSE}
    library(xcms)


    params <- list()
   
    params$CentWave <- CentWaveParam( ppm = 20,
                                      peakwidth =  c(0.05,0.2)*60,
                                      snthresh = 5,
                                      noise = 1500,
                                      prefilter = c(3,1500),
                                      integrate = 2,
                                      mzdiff = -0.001,
                                      verboseColumns = TRUE,
                                      fitgauss = TRUE,
                                      extendLengthMSW = TRUE
    )
```

    
   
#### Grouping for alignment ðŸ•µ
```{r eval=FALSE}
    params$group1 <- PeakDensityParam( sampleGroups = rep(1, length(list.files(path_files_mzML))),
                                       binSize = 0.01,
                                       bw = 2,
                                       minSamples = 1,
                                       minFraction = 0.3,
                                       maxFeatures = 20
    )
```

   
   
#### Alignment ðŸ•µ
```{r eval=FALSE}
    params$PeakAlign <- PeakGroupsParam(  smooth = "loess",
                                          span = 0.6,
                                          minFraction    = 0.8,
                                          family = "gaussian",
                                          extraPeaks = 3
                                          #subset = 
    )
```

   
   
#### Grouping again with stricter condition after alignment ðŸ•µ
```{r eval=FALSE}
    params$group2 <- PeakDensityParam( sampleGroups = rep(1, length(list.files(path_files_mzML))),
                                       binSize = 0.01,
                                       bw = 1.8,
                                       minSamples = 1,
                                       minFraction = 0.6,
                                       maxFeatures = 20
    )
```

   
   
#### Gap filling ðŸ•µ
```{r eval=FALSE}
    params$FillChromPeaksParam <- FillChromPeaksParam(expandMz = 0, 
                                                      expandRt = 0, 
                                                      ppm = 30)
   
```

   
   
#### Conducting XCMS
```{r eval=FALSE}
    raw <- readMSData(list.files(path_files_mzML, full.names = TRUE), 
                      mode = "onDisk")
   
   
   
    source(paste0(path_utils_prepro, "/XCMS.R"))
```

   
   
   
   
   
   
   
   
   
   
## Extraction of MS2-spectra
   The script `3a.Pipeline_extract_MS2.R` is available under the folder of `J:\CBMR\SUN-CBMR-Metabolomics\Workflow\Script\modules\MS2_preprocessing`
   


### Source paths on the server
```{r eval=FALSE}
source("H:/From_SUND/Scripts/utils/utils_MS2_set_up/set_up_paths.R")
```



### Provide the polarity ðŸ•µ
```{r eval=FALSE}
polarity <- "POS" #or "NEG"
```



### Path of XCMSnExp object after conducting XCMS ðŸ•µ
```{r eval=FALSE}
path_rds_xcms_XCMSnExp <- "H:/From_SUND/Scripts/outputs/xcms_XCMSnExp_POS.rds" 
```


   
### Path of storing outputs ðŸ•µ
```{r eval=FALSE}
path_outputs <- "H:/From_SUND/Scripts/outputs"
```

 
   
### Parameters for extracting MS2 spectra ðŸ•µ
#### Extraction: Threshold of rt and m/z for extraction and what type of object return ðŸ•µ
```{r eval=FALSE}
params <- list()
params$expandRt <- 15
params$expandMz <- 0.01
params$return.type <- "Spectra"  #"MSpectra", "list", "List"
```

   
   
### Combining: Threshold of mz, proportion among all samples, type for combining, function for combining mz and intensity ðŸ•µ
```{r eval=FALSE}
# for getting consensus spectra for each feature at each collision energy
params$tolerance <- 0.005
params$peaks <- "intersect"  #"union" #report all peaks from all input spectra 
params$minProp <- 0.7
params$intfun <- median
params$mzfun <- median
```

   
   
### (Optional but recommended) Plot the MS2 spectra âœˆï¸
<div class="Keats_red"> If not, please do not run this line </div>
```{r eval=FALSE}
plot_pdf <- "TRUE"
```

   
   
### (Optional but reconmended) Reduce the number of the MS2 spectra âœˆï¸
<div class="Keats_red"> If not, please do not run these two lines </div>
```{r eval=FALSE}
npeaks_reduce <- "TRUE"
npeaks_remaining <- 60
```



   
### Conduct the extraction of MS2 spectra 
```{r eval=FALSE}
source(paste0(path_utils_prepro, "/extract_MS2.R"))
```


   
   





## (Optional) CAMERA
<font color = "red">If you would like to get more information related to adduct, please run these lines, but you have to have at least 6 samples</font>

   The script `4.(optional)Pipeline_CAMERA.R` is available under the folder of `J:\CBMR\SUN-CBMR-Metabolomics\Workflow\Script\modules\MS2_preprocessing`
   
   
   
### Source paths on the server
```{r eval=FALSE}
source("H:/From_SUND/Scripts/utils/utils_MS2_set_up/set_up_paths.R")
```




### Provide the polarity ðŸ•µ
```{r eval=FALSE}
polarity <- "POS"
```

  

### Path of storing outputs ðŸ•µ
```{r eval=FALSE}
path_outputs <- "H:/From_SUND/Scripts/outputs"
```


   
### Read XCMSnExp object after conducting XCMS ðŸ•µ
```{r eval=FALSE}
path_rds_xcms_XCMSnExp <- "H:/From_SUND/Scripts/outputs/xcms_XCMSnExp_POS.rds" 
```

 
### Parameters for CAMERA ðŸ•µ
#### Grouping ðŸ•µ
```{r eval=FALSE}
params <- list()
params$perfwhm <- 0.6          #percentage of the width of the FWHM (full width at half maximum) of the peak
params$group_intval <- "into"  #the type of intensity value
params$sigma <- 6              #multiplier of the standard deviation
```

   
   
#### correlation ðŸ•µ
```{r eval=FALSE}
params$calcIso <- FALSE      #include isotope detection information for graph clustering
params$calcCiS <- FALSE      #calculate correlation inside samples
params$calsCaS <- TRUE       #calculate correlation across samples
params$cor_eic_th <- 0.7     #correlation threshold for RIC correlation
params$cor_exp_th <- 0.3     #threshold for intensity correlations across samples
params$pval <- 1E-6          #p-value threshold for testing correlation of significance
params$graphMethod <- "lpc"  #clustering method for resulting correlation graph (hcs, lpc)
params$intval_cor <- "into"  #selection of the intensity values
```

   
   
#### find isotopes ðŸ•µ
```{r eval=FALSE}
params$find_isoto_ppm <- 10         #threshold for m/z
params$mzabs <- 0.01                #allowed variance for the search
params$find_isoto_intval <- "into"  #choose intensity values for C12/C13 check
```

   
   
   
#### find adducts ðŸ•µ
```{r eval=FALSE}
params$find_addu_ppm <- 10    
params$mzabs <- 0.01
params$multiplier <- 4         #highest number(n) of allowed clusterion [nM+ion]
   
```


   
### Conduct CAMERA
```{r eval=FALSE}
source(paste0(path_utils_prepro, "/CAMERA.R"))
     
```

    


  
   


