# MS2-Annotation
This chapter consists of: 

1. Submit job of CMN and jobs based on CMN on GNPS (involved uploading files to the server of GNPS) 

2. Submit job of FBMN and jobs based on FBMN on GNPS (involved uploading files to the server of GNPS)

3. Download all results from all submitted jobs and merge into a large table  

4. Compare MS2-experimental data with our in-house library 

5. Merge the results obtained from each GNPS-job and library-match into one table




## MS2-inhouse-library v.s. experimental data
The script `1c.Pipeline_exp_vs_lib.R` is available under the folder of `J:\CBMR\SUN-CBMR-Metabolomics\Workflow\Script\modules\MS2_Annotation`


### Source paths on the server
```{r eval=FALSE}
source("H:/From_SUND/Scripts/utils/utils_MS2_set_up/set_up_paths.R")
```



### Provide polarity (upper case) ðŸ•µ
```{r eval=FALSE}
polarity <- "POS" # "POS" "NEG"
```
 
   
   
### Provide path of preprocessed MS2-spectra file ðŸ•µ
<font color = "red">It is the absolute path by including the file name as the format of `*.mgf`</font>
```{r eval=FALSE}
path_mgf_expMS2 <- "H:/From_SUND/Scripts/outputs/exp_MS2_POS.mgf"
```
  

   
### provide the thresholds ðŸ•µ
They are for m/z and similarity score which is used for cutting off the matches with the scores lower than the threshold
```{r eval=FALSE}
mz_threshold <- 0.01
cor_threshold <- 0.7
```

   
   
### Provide the path of storing output ðŸ•µ
```{r eval=FALSE}
path_outputs <- "H:/From_SUND/Scripts/outputs"
```



### (Optional) Provide the method for comparison âœˆï¸
<div class="Keats"> The default method is `cp_method <- "cosine"`  you could also try other methods for comparison "nspecanglescore", "navdistscore", or "neuclideanscore"</div>
```{r eval=FALSE}
cp_method <- "cosine"
```




### Conduct
```{r eval=FALSE}
if (polarity == "POS") {
  
  path_lib_MS2 <- paste0(path_MS2_lib, "/RP_lib_MS2_60_POS.mgf")
  
} else if (polarity == "NEG") {
    
  path_lib_MS2 <- paste0(path_MS2_lib, "/RP_lib_MS2_60_NEG.mgf")
}
 
source(paste0(path_func, "/lib_vs_exp_MS2.R"))

MS2_vs_exp(path_lib_MS2, path_mgf_expMS2, mz_threshold, cor_threshold, polarity, path_outputs, cp_method)
```

 

















## GNPS-Submit jobs based on CMN
The script `1b.Pipeline_GNPS_upload_submitjobs_based on CMN.R` is available under the folder of `J:\CBMR\SUN-CBMR-Metabolomics\Workflow\Script\modules\MS2_Annotation`

<div class="Keats">The pipeline is for:

1.Uploading files to the server of GNPS.

2.Generating parameters for each job you would like to run.

3.Running CMN (classic molecular network) and a couple of other jobs based on CMN on GNPS.

4.Changing the parameters related to the jobs you would like to run.

5.Please pay attention to the filenames <font color = "red">**no space within each filename**</font>
</div>



### Upload files
#### Source paths on the server and relevant function
```{r eval=FALSE}
source("H:/From_SUND/Scripts/utils/utils_MS2_set_up/set_up_paths.R")
source(paste0(path_func, "/files_by_FTP.R"))
```

 

#### Provide polarity (upper case) ðŸ•µ
```{r eval=FALSE}
polarity <- "POS"
```

  
   

#### Provide project information (only provide the value you want)ðŸ•µ
```{r eval=FALSE}
project_name <- ""
study <- ""
sample_type <- ""
omics <- ""
method <- ""
```

   

   
#### Information related to run jobs on GNPS ðŸ•µ
```{r eval=FALSE}
username <- ""
password <- ""
host <- "massive.ucsd.edu"
email <- ""
```


   
#### Provide the path of storing files without filenames ðŸ•µ
<font color = "red">To be sure only files from unique polarity for running CMN within the provided folder</font>
```{r eval=FALSE}
masterpath <- "H:/From_SUND/Scripts/test/mzML_openms_MS2_POS"
```

   
   
#### Upload files into server (FTP) \n(consistent with the parameters provided above)ðŸ•µ
```{r eval=FALSE}
upload_file_FTP(  masterpath, 
                  list.files(masterpath), 
                  username, 
                  password, 
                  host, 
                  project_name = project_name, 
                  polarity     = polarity, 
                  study        = study, 
                  sample_type  = sample_type, 
                  omics        = omics, 
                  method       = method
               )
```




### Prerequisites before generating parameters and submitting jobs ðŸ•µ
!!! Run the chunk below whenever start running any job
```{r eval=FALSE}
#Provide the path for storing the lists of both parameters and job ids  
path_outputs_params_jobids <- "H:/From_SUND/Scripts/outputs"


#The two lines below are for storing all parameters related to the workflows you will run
list_param_GNPS <- list()
list_jobid_GNPS <- list()
```




### [CMN](https://ccms-ucsd.github.io/GNPSDocumentation/networking/) 
#### Generate parameters ðŸ•µ
```{r eval=FALSE}
parameters_CMN <- list()
parameters_CMN["precursor_ion_mass_tolerance"] <- "0.02"
parameters_CMN["fragment_ion_mass_tolerance"] <- "0.02"
parameters_CMN["min_pairs_cos"] <- "0.7"
parameters_CMN["minimum_matched_fragment_ions"] <- "6"
parameters_CMN["maximum_shift"] <- "500"
parameters_CMN["network_topk"] <- "10"
parameters_CMN["minimum_cluster_size"] <- "2"
parameters_CMN["run_mscluster"] <- "on" 
parameters_CMN["maximum_connected_component_size"] <- "100"
parameters_CMN["library_search_min_matched_peaks"] <- "6"
parameters_CMN["score_threshold"] <- "0.7"
parameters_CMN["search_analogs"] <- "0" 
parameters_CMN["maximum_analog_search_mass_difference"] <- "100" 
parameters_CMN["filter_below_std_dev"] <- "0.0"
parameters_CMN["minimum_peak_intensity"] <- "0.0"
parameters_CMN["filter_precursor_window"] <- "1"
parameters_CMN["filter_library"] <- "1" 
parameters_CMN["filter_peaks_10_50Da_window"] <- "1" 
parameters_CMN["filter_spectra_from_G6_as_blanks_before_networking"] <- "0" 
parameters_CMN["find_related_datasets"] <- "0" 
parameters_CMN["create_cluster_buckets_and_qiime2_biom_pcoa_plots_output"] <- "1" 
parameters_CMN["create_ili_mapping_output"] <- "0"
```

     

#### Submit CMN
```{r eval=FALSE}
source(paste0(path_utils_annotation, "/GNPS_upload_submitjobs.R"))
```




### [Dereplicator](https://ccms-ucsd.github.io/GNPSDocumentation/dereplicator/) 
#### Generate parameters ðŸ•µ
```{r eval=FALSE}
parameters_CMN_Dereplicator <- list()
parameters_CMN_Dereplicator["precursor_ion_mass_tolerance"] <- "0.02"
parameters_CMN_Dereplicator["search_analogs"] <- "on" # if you do not select, just leave it empty like ""
parameters_CMN_Dereplicator["fragment_ion_mass_tolerance"] <- "0.02"
parameters_CMN_Dereplicator["pnp_database"] <- "pnpdatabase" # "dmisam" for "Extended", "combined" for "Regular"
parameters_CMN_Dereplicator["max_charge"] <- "2"
parameters_CMN_Dereplicator["accurate_p_values"] <- "on" # leave it empty, like "", if you do not select it
parameters_CMN_Dereplicator["min_number_of_AA"] <- "5"
parameters_CMN_Dereplicator["max_isotopic_shift"] <- "0" # other options are "1", "2"
parameters_CMN_Dereplicator["adducts_Na"] <- "" # if select, give the value like "on"
parameters_CMN_Dereplicator["adducts_K"] <- ""  # if select, give the value like "on"
parameters_CMN_Dereplicator["max_allowed_modification_mass"] <- "150" 
parameters_CMN_Dereplicator["min_matched_peaks_with_known_compounds"] <- "5"
```

     
#### Submit Dereplicator
```{r eval=FALSE}
source(paste0(path_utils_annotation, "/GNPS_upload_submitjobs.R"))
```




### [Dereplicator plus](https://ccms-ucsd.github.io/GNPSDocumentation/dereplicator%2B/) 
#### Generate parameters ðŸ•µ
```{r eval=FALSE}
parameters_CMN_Dereplicator_plus <- list()
parameters_CMN_Dereplicator_plus["precursor_ion_mass_tolerance"] <- "0.02"
parameters_CMN_Dereplicator_plus["fragment_ion_mass_tolerance"] <- "0.02"
parameters_CMN_Dereplicator_plus["max_charge"] <- "2" # other options are 1 and 3
parameters_CMN_Dereplicator_plus["min_score"] <- "12"
```

     
#### Submit Dereplicator plus
```{r eval=FALSE}
source(paste0(path_utils_annotation, "/GNPS_upload_submitjobs.R"))
```


 

### [NAP](https://ccms-ucsd.github.io/GNPSDocumentation/nap/) 
#### Generate parameters ðŸ•µ  
<font color = "red">\*parameters are different from different polarities</font>
```{r eval=FALSE}
parameters_CMN_NAP <- list()
parameters_CMN_NAP["number_of_a_cluster_index"] <- "0"
parameters_CMN_NAP["cosine_value_to_subselect_inside_a_cluster"] <- "0.7" 
parameters_CMN_NAP["n_first_candidates_for_consensus_score"] <- "10"
parameters_CMN_NAP["use_fusion_result_for_consensus"] <- "on" # if deselect, ""
parameters_CMN_NAP["accuracy_for_exact_mass_candidate_search_ppm"] <- "15"
parameters_CMN_NAP["structure_database"] <- "GNPS,HMDB,SUPNAT,NPAtlas,CHEBI,DRUGBANK,FooDB" 
parameters_CMN_NAP["maximum_number_of_candidate_structures_in_the_graph"] <- "10"
```

     
<font color = "red">Be careful the inputs of parameters depending on the polarity, so only change the inputs related to the polarity you are working on</font>

```{r eval=FALSE}
if (polarity == "POS") {
  
  parameters_CMN_NAP["acquisition_mode"] <- "Positive"
  parameters_CMN_NAP["adduct_ion_type"] <- "[M+H]" # other options are "[M]","[M+NH4]","[M+Na]","[M+K]", "[M+ACN+H]" 
  parameters_CMN_NAP["multiple_adduct_types"] <- "[M+Na]" 

  } else if (polarity == "NEG") {
    parameters_CMN_NAP["acquisition_mode"] <- "Negative" 
    parameters_CMN_NAP["adduct_ion_type"] <- "[M-H]" # other options are "[M+Cl]", "[M+FA-H]"
    parameters_CMN_NAP["multiple_adduct_types"] <- "[M+Cl]"
                
  }   
```

      
#### Submit NAP
```{r eval=FALSE}
source(paste0(path_utils_annotation, "/GNPS_upload_submitjobs.R"))
```


 
  
### [MS2LDA](https://ccms-ucsd.github.io/GNPSDocumentation/ms2lda/) 
#### Generate parameters ðŸ•µ  

<font color = "red">If the polarity is negative mode, recommend to exclude all motif by changing values from "yes" to "no" </font>


```{r eval=FALSE}
parameters_CMN_MS2LDA <- list()
parameters_CMN_MS2LDA["bin_width"] <- "0.01" #other options are 0.005, 0.05, 0.1, 0.5
parameters_CMN_MS2LDA["number_of_lda_iterations"] <- "1000"
parameters_CMN_MS2LDA["minimum_ms2_intensity"] <- "100"
parameters_CMN_MS2LDA["lda_free_motifs"] <- "200"
parameters_CMN_MS2LDA["gnps_motif_inclusion"] <- "yes" #if deselect, "no"
parameters_CMN_MS2LDA["massbank_motif_inclusion"] <- "yes"
parameters_CMN_MS2LDA["urine_motif_inclusion"] <- "yes" 
parameters_CMN_MS2LDA["euphorbia_motif_inclusion"] <- "no"
parameters_CMN_MS2LDA["rhamnaceae_plant_motif_inclusion"] <- "no"
parameters_CMN_MS2LDA["streptomyces_and_salinisporus_motif_inclusion"] <- "no"
parameters_CMN_MS2LDA["photorhabdus_and_xenorhabdus_motif_inclusion"] <- "no" 
parameters_CMN_MS2LDA["user_motif_inclusion"] <- "None" 
parameters_CMN_MS2LDA["overlap_score_threshold"] <- "0.3"
parameters_CMN_MS2LDA["probability_value_threshold"] <- "0.1"
parameters_CMN_MS2LDA["topx_in_node"] <- "5" 
```

     
#### Submit MS2LDA  
```{r eval=FALSE}
source(paste0(path_utils_annotation, "/GNPS_upload_submitjobs.R"))
```




### [MNE (MolNetEnhancer)](https://ccms-ucsd.github.io/GNPSDocumentation/molnetenhancer/)
#### Generate parameters ðŸ•µ  
```{r eval=FALSE}
source(paste0(path_utils_annotation, "/GNPS_upload_submitjobs.R"))

parameters_CMN_MNE <- list()
parameters_CMN_MNE["enter_varquest_id"] <- "None"    # leave it as "None" if this id is not available 

parameters_CMN_MNE["enter_nap_id"] <- list_jobid_GNPS$CMN_NAP_task_id  
parameters_CMN_MNE["enter_gnps_task_id"] <- list_jobid_GNPS$CMN_task_id
parameters_CMN_MNE["enter_Dereplicator_id"] <- list_jobid_GNPS$CMN_Dereplicator_task_id
parameters_CMN_MNE["enter_ms2lda_job_id"] <- list_jobid_GNPS$CMN_MS2LDA_task_id  #Leave it as "None" if this id is not available
```


#### Submit MNE
```{r eval=FALSE}
source(paste0(path_utils_annotation, "/GNPS_upload_submitjobs.R"))
```







### [Merge network polarity](https://ccms-ucsd.github.io/GNPSDocumentation/mergepolarity/)
#### Generate parameters ðŸ•µ

<font color = "red">If it is CMN-based network, the unit of tolerance of rt is **second** </font>
```{r eval=FALSE}
list_param_jobid_MNP <- list()
source(paste0(path_utils_annotation, "/GNPS_upload_submitjobs.R"))


parameters_CMN_MNP <- list()
parameters_CMN_MNP["enter_gnps_positive_network_task_id"] <- list_jobid_MN_both$CMN_task_id_POS    
parameters_CMN_MNP["enter_gnps_negative_network_task_id"] <- list_jobid_MN_both$CMN_task_id_NEG    
parameters_CMN_MNP["enter_a_rt_tolerance_for_aligning_masses_between_two_runs"] <- 10
parameters_CMN_MNP["enter_a_ppm_tolerance_for_aligning_masses_between_two_runs"] <- 30 
```


#### Merge polarities
```{r eval=FALSE}
source(paste0(path_utils_annotation, "/GNPS_upload_submitjobs.R"))
```










## GNPS-Submit jobs based on FBMN
You only need to prepare a reprocessed MS2-spectra as the format of `.mgf` and the corresponding quantification table as the format of `.txt` or `.csv`

<font color = "red">1. Not recommend to preprocess MS2 data by metaboscape. Because 1) Regarding .mgf file, the output is average MS2 spectra across multiple CEs; 2) Regarding .csv file, m/z is not correct</font>

<font color = "red">2. Change the parameters in the sections below related to the workflows you would like to run</font>


### Form quantification table
   The script `0b.Pipeline_quan_table.R` is available under the folder of `J:\CBMR\SUN-CBMR-Metabolomics\Workflow\Script\modules\MS2_Annotation`
   
#### Source paths on the server
```{r eval=FALSE}
source("H:/From_SUND/Scripts/utils/utils_MS2_set_up/set_up_paths.R")
```

 

#### Provide the polarity ðŸ•µ
```{r eval=FALSE}
polarity <- "POS"
```
 

   
#### Path of storing outputs ðŸ•µ
```{r eval=FALSE}
path_output <- "H:/From_SUND/Scripts/outputs"
```

  
   
#### Path of extracted MS2 spectra ðŸ•µ
```{r eval=FALSE}
path_rds_expMS2 <- "H:/From_SUND/Scripts/outputs/exp_MS2_POS.rds" 
```

   
   
#### Path of object after conducting XCMS ðŸ•µ
```{r eval=FALSE}
path_rds_xcms_XCMSnExp <- "H:/From_SUND/Scripts/outputs/xcms_XCMSnExp_POS.rds" 
```
  
   
   
#### (Optional) Path of object CAMERA (if conduct CAMERA) âœˆï¸
<font color = "red">If you have run CAMERA, please provide the path, otherwise, skip running the line below</font>
```{r eval=FALSE}
path_rds_cam_xsAnnotate <- "H:/From_SUND/Scripts/outputs/cam_xsAnnotate_POS.rds" 
```



#### Conduct to get quantification table for FBMN on GNPS
```{r eval=FALSE}
if (exists("path_rds_cam_xsAnnotate")) {
  
  #Type of intensity value to extract from object of xcms_XCMSnExp
  feature_int <- "into"
     
}
   
   
source(paste0(path_utils_annotation, "/quan_table.R"))
```






### Upload files, generate parameters, and submit jobs
The script `1b.Pipeline_GNPS_upload_submitjobs_based on FBMN.R` is available under the folder of `J:\CBMR\SUN-CBMR-Metabolomics\Workflow\Script\modules\MS2_Annotation`

<div class="Keats">The pipeline is for:

1.Uploading files to the server of GNPS. 

2.Generating parameters for each job you would like to run.

3.Running FBMN (feature based molecular network) and a couple of other jobs based on FBMN on GNPS. 

<font color = "red">4.Changing the parameters related to the jobs you would like to run.</font>
</div>



#### Upload files
##### Source paths on the server and relevant function
```{r eval=FALSE}
source("H:/From_SUND/Scripts/utils/utils_MS2_set_up/set_up_paths.R")
source(paste0(path_func, "/files_by_FTP.R"))
```



##### Provide polarity (upper case) ðŸ•µ
```{r eval=FALSE}
polarity <- "POS"
```
   
   
   
##### Provide project information ðŸ•µ
```{r eval=FALSE}
project_name <- "workflow_test" 
study <- "1"            #what ordinal number comes current samples? e.g. "1", or "2",...
sample_type <- "serum"
omics <- "metabolomics"
method <- "RP"
```

   
   
##### Information related to run jobs on GNPS or computer room ðŸ•µ
```{r eval=FALSE}
username <- "xx"
password <- "xx"
host <- "massive.ucsd.edu"
email <- "xx"
```

      
   
##### Provide the path of storing files without filenames  ðŸ•µ
```{r eval=FALSE}
masterpath <- "H:/From_SUND/Scripts/outputs"
```

    


##### Provide the filenames ðŸ•µ
`.txt` or `.csv`of quantification table and `.mgf` file of MS2 spectra 
```{r eval=FALSE}
filenames <- c("quantable_POS.txt", "exp_MS2_POS.mgf")

```



##### Provide method you used for preprocessing the MS2-spectra data ðŸ•µ
```{r eval=FALSE}
prep_method <- "XCMS3" #other options are illustrated within the function in the file of "submit_jobs_to_GNPS.R"
```



##### Upload files into server (FTP)
```{r eval=FALSE}
upload_file_FTP(  masterpath, 
                  filenames, 
                  username, 
                  password, 
                  host, 
                  project_name,
                  polarity, 
                  study       = study, 
                  sample_type = sample_type, 
                  omics       = omics, 
                  method      = method
               )
```
  
  


#### Prerequisites before generating parameters and submitting jobs ðŸ•µ
```{r eval=FALSE}
#Provide the path for storing the lists of both parameters and job ids  
path_outputs_params_jobids <- "H:/From_SUND/Scripts/outputs"


#The two lines below are for storing all parameters related to the workflows you will run
list_param_GNPS <- list()
list_jobid_GNPS <- list()
```




#### [FBMN](https://ccms-ucsd.github.io/GNPSDocumentation/featurebasedmolecularnetworking/)
##### Generate parameters ðŸ•µ
```{r eval=FALSE}
parameters_FBMN <- list()
parameters_FBMN["precursor_ion_mass_tolerance"] <- "0.02"
parameters_FBMN["fragment_ion_mass_tolerance"] <- "0.02"
parameters_FBMN["min_pairs_cos"] <- "0.7"
parameters_FBMN["minimum_matched_fragment_ions"] <- "6"
parameters_FBMN["maximum_shift"] <- "500"
parameters_FBMN["network_topk"] <- "10"
parameters_FBMN["maximum_connected_component_size"] <- "100"
parameters_FBMN["library_search_min_matched_peaks"] <- "6"
parameters_FBMN["score_threshold"] <- "0.7"
parameters_FBMN["search_analogs"] <- "0" # don't search/ "1" search
parameters_FBMN["maximum_analog_search_mass_difference"] <- "100" # it only works once select the search analog
parameters_FBMN["top_results_to_report_per_query"] <- "1"
parameters_FBMN["minimum_peak_intensity"] <- "0.0"
parameters_FBMN["filter_precursor_window"] <- "1" # filter / "0" don't filter
parameters_FBMN["filter_library"] <- "1" # filter / "0" don't filter
parameters_FBMN["filter_peaks_10_50Da_window"] <- "1" # filter / "0" don't filter
parameters_FBMN["normalization_per_file"] <- "None" # represent no normalization, the other option is "RowSum"
parameters_FBMN["aggregation_method_for_peak_abundances_per_group"] <- "Mean" # another option is "Sum"
parameters_FBMN["pcoa_distance_metric"] <- "cosine" # other options are "braycurtis", "euclidean", "jaccard"
parameters_FBMN["metadata_column_to_compare"] <- "None"
parameters_FBMN["run_stats_and_plots"] <- "No" # other option is "Yes"
parameters_FBMN["metadata_field_to_compare_1"] <- "None"
parameters_FBMN["metadata_field_to_compare_2"] <- "None"
parameters_FBMN["metadata_column_to_facet"] <- "None"
parameters_FBMN["run_Dereplicator"] <- "1" # "0" represent don't run and "1" represents run
```


##### Submit FBMN
```{r eval=FALSE}
source(paste0(path_utils_annotation, "/GNPS_upload_submitjobs.R"))
```

     
      
#### [Dereplicator plus](https://ccms-ucsd.github.io/GNPSDocumentation/dereplicator%2B/)
##### Generate parameters ðŸ•µ
```{r eval=FALSE}
parameters_FBMN_Dereplicator_plus <- list()
parameters_FBMN_Dereplicator_plus["precursor_ion_mass_tolerance"] <- "0.02"
parameters_FBMN_Dereplicator_plus["fragment_ion_mass_tolerance"] <- "0.02"
parameters_FBMN_Dereplicator_plus["max_charge"] <- "2" # other options are 1 and 3
parameters_FBMN_Dereplicator_plus["min_score"] <- "12"
```


##### Submit Dereplicator plus
```{r eval=FALSE}
source(paste0(path_utils_annotation, "/GNPS_upload_submitjobs.R"))
```
     
  
    

#### [NAP](https://ccms-ucsd.github.io/GNPSDocumentation/nap/)
<font color = "red">\*parameters are different from different polarities</font>

##### Generate parameters ðŸ•µ
```{r eval=FALSE}
parameters_FBMN_NAP <- list()
parameters_FBMN_NAP["number_of_a_cluster_index"] <- "0"
parameters_FBMN_NAP["cosine_value_to_subselect_inside_a_cluster"] <- "0.7" 
parameters_FBMN_NAP["n_first_candidates_for_consensus_score"] <- "10"
parameters_FBMN_NAP["use_fusion_result_for_consensus"] <- "on" # if deselect, ""
parameters_FBMN_NAP["accuracy_for_exact_mass_candidate_search_ppm"] <- "15"
parameters_FBMN_NAP["structure_database"] <- "GNPS,HMDB,SUPNAT,NPAtlas,CHEBI,DRUGBANK,FooDB" 
parameters_FBMN_NAP["maximum_number_of_candidate_structures_in_the_graph"] <- "10"
```

     
<font color = "red">Be careful the inputs of parameters depending on the polarity, so only change the inputs related to the polarity you are working on</font>
```{r eval=FALSE}
if (polarity == "POS") {
  
  parameters_FBMN_NAP["acquisition_mode"] <- "Positive"
  parameters_FBMN_NAP["adduct_ion_type"] <- "[M+H]" # other options are "[M]", "[M+NH4]", "[M+Na]", "[M+K]", "[M+ACN+H]" 
  parameters_FBMN_NAP["multiple_adduct_types"] <- "[M+Na]" 

} else if (polarity == "NEG") {
  
  parameters_FBMN_NAP["acquisition_mode"] <- "Negative" 
  parameters_FBMN_NAP["adduct_ion_type"] <- "[M-H]" # other options are "[M+Cl]", "[M+FA-H]"
  parameters_FBMN_NAP["multiple_adduct_types"] <- "[M+Cl]"
                
}  
```


##### Submit NAP
```{r eval=FALSE}
source(paste0(path_utils_annotation, "/GNPS_upload_submitjobs.R"))
```

     



#### (Optional) [MS2LDA](https://ccms-ucsd.github.io/GNPSDocumentation/ms2lda/) âœˆï¸ 
##### Generate parameters ðŸ•µ
```{r eval=FALSE}
parameters_FBMN_MS2LDA <- list()
parameters_FBMN_MS2LDA["bin_width"] <- "0.01" #other options are 0.005, 0.05, 0.1, 0.5
parameters_FBMN_MS2LDA["number_of_lda_iterations"] <- "1000"
parameters_FBMN_MS2LDA["minimum_ms2_intensity"] <- "100"
parameters_FBMN_MS2LDA["lda_free_motifs"] <- "200"
parameters_FBMN_MS2LDA["gnps_motif_inclusion"] <- "yes" #if deselect, "no"
parameters_FBMN_MS2LDA["massbank_motif_inclusion"] <- "yes"
parameters_FBMN_MS2LDA["urine_motif_inclusion"] <- "yes" 
parameters_FBMN_MS2LDA["euphorbia_motif_inclusion"] <- "no"
parameters_FBMN_MS2LDA["rhamnaceae_plant_motif_inclusion"] <- "no"
parameters_FBMN_MS2LDA["streptomyces_and_salinisporus_motif_inclusion"] <- "no"
parameters_FBMN_MS2LDA["photorhabdus_and_xenorhabdus_motif_inclusion"] <- "no" 
parameters_FBMN_MS2LDA["user_motif_inclusion"] <- "None" 
parameters_FBMN_MS2LDA["overlap_score_threshold"] <- "0.3"
parameters_FBMN_MS2LDA["probability_value_threshold"] <- "0.1"
parameters_FBMN_MS2LDA["topx_in_node"] <- "5" 
```


##### Submit MS2LDA 
```{r eval=FALSE}
source(paste0(path_utils_annotation, "/GNPS_upload_submitjobs.R"))
```



  
  
#### [MNE (MolNetEnhancer)](https://ccms-ucsd.github.io/GNPSDocumentation/molnetenhancer/)
##### Generate parameters ðŸ•µ  
```{r eval=FALSE}
source(paste0(path_utils_annotation, "/GNPS_upload_submitjobs.R"))

parameters_FBMN_MNE <- list()
parameters_FBMN_MNE["enter_varquest_id"] <- "None"    # leave it as "None" if this id is not available 


parameters_FBMN_MNE["enter_nap_id"] <- list_jobid_GNPS$FBMN_NAP_task_id
parameters_FBMN_MNE["enter_gnps_task_id"] <- list_jobid_GNPS$FBMN_task_id
parameters_FBMN_MNE["enter_ms2lda_job_id"] <- list_jobid_GNPS$FBMN_MS2LDA_task_id # or "None"
```
``
   
   

##### Submit MNE
```{r eval=FALSE}
source(paste0(path_utils_annotation, "/GNPS_upload_submitjobs.R"))
```




 


### [Merge network polarity](https://ccms-ucsd.github.io/GNPSDocumentation/mergepolarity/)
#### Generate parameters ðŸ•µ

<font color = "red">If it is FBMN-based network, the unit of tolerance of rt is **minute** </font>
```{r eval=FALSE}
list_param_jobid_MNP <- list()
source(paste0(path_utils_annotation, "/GNPS_upload_submitjobs.R"))


parameters_FBMN_MNP <- list()
parameters_FBMN_MNP["enter_gnps_positive_network_task_id"] <- list_jobid_MN_both$FBMN_task_id_POS    
parameters_FBMN_MNP["enter_gnps_negative_network_task_id"] <- list_jobid_MN_both$FBMN_task_id_NEG    
parameters_FBMN_MNP["enter_a_rt_tolerance_for_aligning_masses_between_two_runs"] <- 0.1
parameters_FBMN_MNP["enter_a_ppm_tolerance_for_aligning_masses_between_two_runs"] <- 20 
```


#### Merge polarities
```{r eval=FALSE}
source(paste0(path_utils_annotation, "/GNPS_upload_submitjobs.R"))
```

















## GNPS-Download jobs 
The script `2.Pipeline_GNPS_download_jobs.R` is available under the folder of `J:\CBMR\SUN-CBMR-Metabolomics\Workflow\Script\modules\MS2_Annotation`

### Source paths on the server ðŸ•µ
```{r eval=FALSE}
source("H:/From_SUND/Scripts/utils/utils_MS2_set_up/set_up_paths.R")
```
 


### Provide polarity (upper case) ðŸ•µ
```{r eval=FALSE}
polarity <- "POS"
```



### Provide the path of storing downloaded files ðŸ•µ
```{r eval=FALSE}
download_path <- "H:/From_SUND/Scripts/outputs"
```
   


### Provide project information (only run the line with value you provide)ðŸ•µ
```{r eval=FALSE}
project_name <- ""
study <- ""
sample_type <- ""
omics <- ""
method <- ""
```

   

### Provide the absolute path of "list of job ids" by including the name of that list ðŸ•µ
<font color = "red">name should start with **list_jobid_GNPS**</font>
```{r eval=FALSE}
path_list <- "H:/From_SUND/Scripts/outputs/jobids_CMN_based_workflow_test_1_serum_metabolomics_RF_POS.rds"
```

 

### Download results from the list of job ids
```{r eval=FALSE}
list_jobid_GNPS <- readRDS(path_list)
source(paste0(path_utils_annotation, "/GNPS_downloadjobs.R"))
```
   
      
      
      
### Provide the absolute path of "list_param_jobid_MNP" by including the name of that list ðŸ•µ
<font color = "red">name should start with **list_param_jobid_MNP**</font>
```{r eval=FALSE}
path_jobid_MNP <- "H:/From_SUND/Scripts/outputs/list_param_jobid_MNP_xx_both.rds"
```



### Download result of merging networks from both polarities
```{r eval=FALSE}
list_jobid_GNPS <- readRDS(path_jobid_MNP)
source(paste0(path_utils_annotation, "/GNPS_downloadjobs.R"))
```
   
      















## Merge results from different source
### Merging outputs from jobs have run on GNPS into a table
The script `3.Pipeline_merge_outputs_from_GNPS.R` is available under the folder of `J:\CBMR\SUN-CBMR-Metabolomics\Workflow\Script\modules\MS2_Annotation`


#### Source paths on the server and relevant function 
```{r eval=FALSE}
source("H:/From_SUND/Scripts/utils/utils_MS2_set_up/set_up_paths.R")
source(paste0(path_func, "/Merge_outputs_from_GNPS.R"))
```

 

#### Provide the path of storing files downloaded from GNPS ðŸ•µ
<font color = "red">The path should be end with **gnps_outputs**</font>
```{r eval=FALSE}
path_downloaded_files <- "H:/From_SUND/Scripts/outputs/workflow_test_1_serum_metabolomics_RF/gnps_outputs"
```



#### Provide the absolute path of "list of job ids" by including the name of that list  ðŸ•µ
<font color = "red">name should start with **list_jobid_GNPS**</font>
```{r eval=FALSE}
path_list <- "H:/From_SUND/Scripts/outputs/jobids_CMN_workflow_test_1_serum_metabolomics_RF_POS.rds"

```



#### Provide path for storing the merged result ðŸ•µ
```{r eval=FALSE}
path_outputs <- "H:/From_SUND/Scripts/outputs"
```  



#### Provide which method did you use for preprocessing MS2 data ðŸ•µ
<font color = "red">If you run jobs based on CMN, skip running the line below</font>
```{r eval=FALSE}
prep_method <- "XCMS3"
```



#### Provide polarity (upper case) ðŸ•µ
```{r eval=FALSE}
polarity <- "POS"
```


#### Provide what workflow based ðŸ•µ
```{r eval=FALSE}
workflow_based <- "CMN" # or "FBMN"
```


#### Conduct
```{r eval=FALSE}
library(dplyr)

list_jobid <- readRDS(path_list)
workflow_all <- names(list_jobid) %>% gsub("_task_id", "",.) 
workflow <- workflow_all[grepl(workflow_based, workflow_all)] %>% strsplit("[A-Z]+_") %>% unlist() %>% unique() %>% na_if("") %>% na.omit() 

if (workflow_based == "FBMN") {
  
  Merge_outputs_from_GNPS(path_downloaded_files, prep_method, workflow, polarity, path_outputs)
  
} else if (workflow_based == "CMN") {
  
  Merge_outputs_from_GNPS(path_downloaded_files, NULL, workflow, polarity, path_outputs)
  
}


```


   





#### Merge library-match into GNPS-match
The script `4.Pipeline_merge_lib-match_GNPS-match.R` is available under the folder of `J:\CBMR\SUN-CBMR-Metabolomics\Workflow\Script\modules\MS2_Annotation`

<font color = "red"> It is more precise to merge the result from library-match with the results from FBMN-based jobs on GNPS</font>


##### Source paths on the server
```{r eval=FALSE}
source("H:/From_SUND/Scripts/utils/utils_MS2_set_up/set_up_paths.R")
```


##### Provide path of excel file of storing matched records and sheet names ðŸ•µ
The file name should be like `MS2-match-outputs.xlsx` and please provide the absolute path
```{r eval = FALSE}
path_MS2_match <- "H:/From_SUND/Scripts/outputs/MS2-match-outputs.xlsx"
sheetName_GNPS <- "GNPS_summary_based_FBMN_POS"
sheetName_lib <- "MS2-lib-vs-exp_cosine_POS"
```



##### Provide the polarity (upper case) ðŸ•µ
```{r eval = FALSE}
polarity <- "POS"
```



##### Provide the path for storing output ðŸ•µ
```{r eval = FALSE}
path_output <- "H:/From_SUND/Scripts/outputs"
```



##### Conduct
```{r eval = FALSE}
source(paste0(path_utils_annotation, "/merge_lib-match_GNPS-match.R"))
```

      