# MS2-Annotation
This chapter consists of:
1. Submit job of CMN and jobs based on CMN on GNPS (involved uploading files to the server of GNPS)
2. Submit job of FBMN and jobs based on FBMN on GNPS (involved uploading files to the server of GNPS)
3. Compare MS2-experimental data with our in-house library
4. Download all results from all submitted jobs
5. Merge the results from each job





## GNPS-Submit jobs based on CMN
The script `1b.Pipeline_GNPS_upload_submitjobs_based on CMN.R` is available under the folder of `J:\CBMR\SUN-CBMR-Metabolomics\Workflow\Script\modules\MS2_Annotation`

<div class="Keats">The pipeline is for: $\\$
1.Uploading files to the server of GNPS. $\\$
2.Generating parameters for each job you would like to run. $\\$
3.Running CMN (classice molecular network) and a couple of other jobs based on CMN on GNPS. $\\$
<div class="Keats_red">4.Changing the parameters related to the jobs you would like to run.</div>
</div>



### Upload files
#### Source paths on the server and relevant function
```{r}
source("H:/From_SUND/Scripts/utils/utils_MS2_set_up/set_up_paths.R")
source(paste0(path_func, "/files_by_FTP.R"))
```

 

#### Provide polarity (upper case)
```{r}
polarity <- "NEG"
```

  
   

#### Provide project information
```{r}
project_name <- ""
round <- ""
sample_type <- ""
omics <- ""
method <- ""
```

   

   
#### Information related to run jobs on GNPS or computer room
```{r}
username <- ""
password <- ""
host <- ""
email <- ""
```


   
#### Provide the path of storing files without filenames
<font color = "red">To be sure only files for running CMN from unique polarity within the provided folder</font>
```{r}
masterpath <- ""
```

   
   
#### Upload files into server (FTP)
```{r}
upload_file_FTP(masterpath, list.files(masterpath), username, password, host, project_name, round, sample_type, omics, method, polarity)
```




### Prerequisites before generating parameters and submitting jobs ðŸ•µ
```{r eval=FALSE}
#Provide the path for storing the lists of both parameters and job ids  
path_outputs_params_jobids <- "H:/From_SUND/Scripts/outputs"


#The two lines below are for storing all parameters related to the workflows you will run
list_param <- list()
list_jobid <- list()
```




### CMN ðŸ•µ
#### Generate parameters ðŸ•µ
```{r eval=FALSE}
parameters_CMN <- list()
parameters_CMN["precursor_ion_mass_tolerance"] <- "0.02"
parameters_CMN["fragment_ion_mass_tolerance"] <- "0.02"
parameters_CMN["min_pairs_cos"] <- "0.7"
parameters_CMN["minimum_matched_fragment_ions"] <- "6"
parameters_CMN["maximum_shift"] <- "500"
parameters_CMN["network_topk"] <- "10"
parameters_CMN["minimum_cluster_size"] <- "2"
parameters_CMN["run_mscluster"] <- "on" 
parameters_CMN["maximum_connected_component_size"] <- "100"
parameters_CMN["library_search_min_matched_peaks"] <- "6"
parameters_CMN["score_threshold"] <- "0.7"
parameters_CMN["search_analogs"] <- "0" 
parameters_CMN["maximum_analog_search_mass_difference"] <- "100" 
parameters_CMN["filter_below_std_dev"] <- "0.0"
parameters_CMN["minimum_peak_intensity"] <- "0.0"
parameters_CMN["filter_precursor_window"] <- "1"
parameters_CMN["filter_library"] <- "1" 
parameters_CMN["filter_peaks_10_50Da_window"] <- "1" 
parameters_CMN["filter_spectra_from_G6_as_blanks_before_networking"] <- "0" 
parameters_CMN["find_related_datasets"] <- "0" 
parameters_CMN["create_cluster_buckets_and_qiime2_biom_pcoa_plots_output"] <- "1" 
parameters_CMN["create_ili_mapping_output"] <- "0"
```

     

#### Submit CMN
```{r eval=FALSE}
source(paste0(path_utils_annotation, "/GNPS_upload_submitjobs.R"))
```




### Dereplicator (after CMN done) ðŸ•µ
#### Generate parameters ðŸ•µ
```{r eval=FALSE}
parameters_CMN_Dereplicator <- list()
parameters_CMN_Dereplicator["precursor_ion_mass_tolerance"] <- "0.02"
parameters_CMN_Dereplicator["search_analogs"] <- "on" # if you do not select, just leave it empty like ""
parameters_CMN_Dereplicator["fragment_ion_mass_tolerance"] <- "0.02"
parameters_CMN_Dereplicator["pnp_database"] <- "pnpdatabase" # "dmisam" for "Extended", "combined" for "Regular"
parameters_CMN_Dereplicator["max_charge"] <- "2"
parameters_CMN_Dereplicator["accurate_p_values"] <- "on" # leave it empty, like "", if you do not select it
parameters_CMN_Dereplicator["min_number_of_AA"] <- "5"
parameters_CMN_Dereplicator["max_isotopic_shift"] <- "0" # other options are "1", "2"
parameters_CMN_Dereplicator["adducts_Na"] <- "" # if select, give the value like "on"
parameters_CMN_Dereplicator["adducts_K"] <- ""  # if select, give the value like "on"
parameters_CMN_Dereplicator["max_allowed_modification_mass"] <- "150" 
parameters_CMN_Dereplicator["min_matched_peaks_with_known_compounds"] <- "5"
```

     
#### Submit Dereplicator
```{r eval=FALSE}
source(paste0(path_utils_annotation, "/GNPS_upload_submitjobs.R"))
```




### Dereplicator plus ðŸ•µ
#### Generate parameters ðŸ•µ
```{r eval=FALSE}
parameters_CMN_Dereplicator_plus <- list()
parameters_CMN_Dereplicator_plus["precursor_ion_mass_tolerance"] <- "0.02"
parameters_CMN_Dereplicator_plus["fragment_ion_mass_tolerance"] <- "0.02"
parameters_CMN_Dereplicator_plus["max_charge"] <- "2" # other options are 1 and 3
parameters_CMN_Dereplicator_plus["min_score"] <- "12"
```

     
#### Submit Dereplicator plus
```{r eval=FALSE}
source(paste0(path_utils_annotation, "/GNPS_upload_submitjobs.R"))
```


 

### NAP ðŸ•µ
#### Generate parameters ðŸ•µ  
<font color = "red">\*parameters are different from different polarities</font>
```{r eval=FALSE}
parameters_CMN_NAP <- list()
parameters_CMN_NAP["number_of_a_cluster_index"] <- "0"
parameters_CMN_NAP["cosine_value_to_subselect_inside_a_cluster"] <- "0.7" 
parameters_CMN_NAP["n_first_candidates_for_consensus_score"] <- "10"
parameters_CMN_NAP["use_fusion_result_for_consensus"] <- "on" # if deselect, ""
parameters_CMN_NAP["accuracy_for_exact_mass_candidate_search_ppm"] <- "15"
parameters_CMN_NAP["structure_database"] <- "GNPS,HMDB,SUPNAT,NPAtlas,CHEBI,DRUGBANK,FooDB" 
parameters_CMN_NAP["maximum_number_of_candidate_structures_in_the_graph"] <- "10"
```

     
<font color = "red">Be careful the inputs of parameters depending on the polarity, so only change the inputs related to the polarity you are working on</font>

```{r eval=FALSE}
if (polarity == "POS") {
  
  parameters_CMN_NAP["acquisition_mode"] <- "Positive"
  parameters_CMN_NAP["adduct_ion_type"] <- "[M+H]" # other options are "[M]","[M+NH4]","[M+Na]","[M+K]", "[M+ACN+H]" 
  parameters_CMN_NAP["multiple_adduct_types"] <- "[M+Na]" 

  } else if (polarity == "NEG") {
    parameters_CMN_NAP["acquisition_mode"] <- "Negative" 
    parameters_CMN_NAP["adduct_ion_type"] <- "[M-H]" # other options are "[M+Cl]", "[M+FA-H]"
    parameters_CMN_NAP["multiple_adduct_types"] <- "[M+Cl]"
                
  }   
```

      
#### Submit NAP
```{r eval=FALSE}
source(paste0(path_utils_annotation, "/GNPS_upload_submitjobs.R"))
```


 
  
### MS2LDA ðŸ•µ
#### Generate parameters ðŸ•µ    
```{r eval=FALSE}
parameters_CMN_MS2LDA <- list()
parameters_CMN_MS2LDA["bin_width"] <- "0.01" #other options are 0.005, 0.05, 0.1, 0.5
parameters_CMN_MS2LDA["number_of_lda_iterations"] <- "1000"
parameters_CMN_MS2LDA["minimum_ms2_intensity"] <- "100"
parameters_CMN_MS2LDA["lda_free_motifs"] <- "200"
parameters_CMN_MS2LDA["gnps_motif_inclusion"] <- "yes" #if deselect, "no"
parameters_CMN_MS2LDA["massbank_motif_inclusion"] <- "yes"
parameters_CMN_MS2LDA["urine_motif_inclusion"] <- "yes" 
parameters_CMN_MS2LDA["euphorbia_motif_inclusion"] <- "no"
parameters_CMN_MS2LDA["rhamnaceae_plant_motif_inclusion"] <- "no"
parameters_CMN_MS2LDA["streptomyces_and_salinisporus_motif_inclusion"] <- "no"
parameters_CMN_MS2LDA["photorhabdus_and_xenorhabdus_motif_inclusion"] <- "no" 
parameters_CMN_MS2LDA["user_motif_inclusion"] <- "None" 
parameters_CMN_MS2LDA["overlap_score_threshold"] <- "0.3"
parameters_CMN_MS2LDA["probability_value_threshold"] <- "0.1"
parameters_CMN_MS2LDA["topx_in_node"] <- "5" 
```

     
#### Submit MS2LDA  
```{r eval=FALSE}
source(paste0(path_utils_annotation, "/GNPS_upload_submitjobs.R"))
```




### MNE (molnetenhancer) ðŸ•µ
#### Generate parameters ðŸ•µ  
```{r eval=FALSE}
parameters_CMN_MNE <- list()
parameters_CMN_MNE["enter_varquest_id"] <- "None"    # leave it as "None" if this id is not available 

     #If ids are not available, please provide them
parameters_CMN_MNE["enter_nap_id"] <- CMN_NAP_task_id  
parameters_CMN_MNE["enter_gnps_task_id"] <- CMN_task_id
parameters_CMN_MNE["enter_Dereplicator_id"] <- CMN_Dereplicator_task_id
parameters_CMN_MNE["enter_ms2lda_job_id"] <- CMN_MS2LDA_task_id  # ms2lda_task_id_pos$ms2lda. Leave it as "None" if this id is not available
```


#### Submit MNE
```{r eval=FALSE}
source(paste0(path_utils_annotation, "/GNPS_upload_submitjobs.R"))
```















## GNPS-Submit jobs based on FBMN
You only need to prepare a reprocessed MS2-spectra as the format of `.mgf` and the corresponding quantification table as the format of `.txt`

<font color = "red">change the parameters in the sections below related to the workflows you would like to run</font>


### Form quantification table
   The script `0b.Pipeline_quan_table.R` is available under the folder of `J:\CBMR\SUN-CBMR-Metabolomics\Workflow\Script\modules\MS2_Annotation`
   
#### Source paths on the server
```{r eval=FALSE}
source("H:/From_SUND/Scripts/utils/utils_MS2_set_up/set_up_paths.R")
```

 

#### Provide the polarity ðŸ•µ
```{r eval=FALSE}
polarity <- "POS"
```
 

   
#### Path of storing outputs ðŸ•µ
```{r eval=FALSE}
path_outputs <- "H:/From_SUND/Scripts/outputs"
```

  
   
#### Path of extracted MS2 spectra ðŸ•µ
```{r eval=FALSE}
path_rds_expMS2 <- "H:/From_SUND/Scripts/outputs/exp_MS2_POS.rds" 
```

   
   
#### Path of object after conducting XCMS ðŸ•µ
```{r eval=FALSE}
path_rds_xcms_XCMSnExp <- "H:/From_SUND/Scripts/outputs/xcms_XCMSnExp_POS.rds" 
```
  
   
   
#### (Optional) Path of object CAMERA (if conduct CAMERA) âœˆï¸
<font color = "red">If you have run CAMERA, please provide the path, otherwise, skip running the line below</font>
```{r eval=FALSE}
path_rds_cam_xsAnnotate <- "H:/From_SUND/Scripts/outputs/cam_xsAnnotate_POS.rds" 
```



#### Conduct to get quantification table for FBMN on GNPS
```{r eval=FALSE}
if (exists("path_rds_cam_xsAnnotate")) {
  
  #Type of intensity value to extract from object of xcms_XCMSnExp
  feature_int <- "into"
     
}
   
   
if (grepl("ku_00007", path_rds_expMS2)) {
  
  source("")
     
} else {source(paste0(path_utils_annotation, "/quan_table.R"))}
```






### Upload files, generate parameters, and submit jobs
The script `1b.Pipeline_GNPS_upload_submitjobs_based on FBMN.R` is available under the folder of `J:\CBMR\SUN-CBMR-Metabolomics\Workflow\Script\modules\MS2_Annotation`

<div class="Keats">The pipeline is for: $\\$
1.Uploading files to the server of GNPS. $\\$
2.Generating parameters for each job you would like to run. $\\$
3.Running FBMN (feature based molecular network) and a couple of other jobs based on FBMN on GNPS. $\\$
<div class="Keats_red">4.Changing the parameters related to the jobs you would like to run.</div>
</div>



#### Upload files
##### Source paths on the server and relevant function
```{r eval=FALSE}
source("H:/From_SUND/Scripts/utils/utils_MS2_set_up/set_up_paths.R")
source(paste0(path_func, "/files_by_FTP.R"))
```



##### Provide polarity (upper case) ðŸ•µ
```{r eval=FALSE}
polarity <- "POS"
```
   
   
   
##### Provide project information ðŸ•µ
```{r eval=FALSE}
project_name <- "workflow_test" 
round <- "1"            #what ordinal number comes current samples? e.g. "1", or "2",...
sample_type <- "serum"
omics <- "metabolomics"
method <- "RP"
```

   
   
##### Information related to run jobs on GNPS or computer room ðŸ•µ
```{r eval=FALSE}
username <- "cherish_199271"
password <- ""
host <- "massive.ucsd.edu"
email <- ""
```

      
   
##### Provide the path of storing files without filenames  ðŸ•µ
```{r eval=FALSE}
masterpath <- "H:/From_SUND/Scripts/outputs"
```

    


##### Provide the filenames ðŸ•µ
`.txt` of quantification table and `.mgf` file of MS2 spectra 
```{r eval=FALSE}
filenames <- c("quantable_POS.txt", "exp_MS2_POS.mgf")

```



##### Provide method you used for preprocessing the MS2-spectra data ðŸ•µ
```{r eval=FALSE}
prep_method <- "XCMS3" #other options are illustrated within the function in the file of "submit_jobs_to_GNPS.R"
```



##### Upload files into server (FTP)
```{r eval=FALSE}
upload_file_FTP(masterpath, filenames, username, password, host, project_name, round, sample_type, omics, method, polarity)
```
  
  


#### Prerequisites before generating parameters and submitting jobs ðŸ•µ
```{r eval=FALSE}
#Provide the path for storing the lists of both parameters and job ids  
path_outputs_params_jobids <- "H:/From_SUND/Scripts/outputs"


#The two lines below are for storing all parameters related to the workflows you will run
list_param <- list()
list_jobid <- list()
```




#### FBMN ðŸ•µ
##### Generate parameters ðŸ•µ
```{r eval=FALSE}
parameters_FBMN <- list()
parameters_FBMN["precursor_ion_mass_tolerance"] <- "0.02"
parameters_FBMN["fragment_ion_mass_tolerance"] <- "0.02"
parameters_FBMN["min_pairs_cos"] <- "0.7"
parameters_FBMN["minimum_matched_fragment_ions"] <- "6"
parameters_FBMN["maximum_shift"] <- "500"
parameters_FBMN["network_topk"] <- "10"
parameters_FBMN["maximum_connected_component_size"] <- "100"
parameters_FBMN["library_search_min_matched_peaks"] <- "6"
parameters_FBMN["score_threshold"] <- "0.7"
parameters_FBMN["search_analogs"] <- "0" # don't search/ "1" search
parameters_FBMN["maximum_analog_search_mass_difference"] <- "100" # it only works once select the search analog
parameters_FBMN["top_results_to_report_per_query"] <- "1"
parameters_FBMN["minimum_peak_intensity"] <- "0.0"
parameters_FBMN["filter_precursor_window"] <- "1" # filter / "0" don't filter
parameters_FBMN["filter_library"] <- "1" # filter / "0" don't filter
parameters_FBMN["filter_peaks_10_50Da_window"] <- "1" # filter / "0" don't filter
parameters_FBMN["normalization_per_file"] <- "None" # represent no normalization, the other option is "RowSum"
parameters_FBMN["aggregation_method_for_peak_abundances_per_group"] <- "Mean" # another option is "Sum"
parameters_FBMN["pcoa_distance_metric"] <- "cosine" # other options are "braycurtis", "euclidean", "jaccard"
parameters_FBMN["metadata_column_to_compare"] <- "None"
parameters_FBMN["run_stats_and_plots"] <- "No" # other option is "Yes"
parameters_FBMN["metadata_field_to_compare_1"] <- "None"
parameters_FBMN["metadata_field_to_compare_2"] <- "None"
parameters_FBMN["metadata_column_to_facet"] <- "None"
parameters_FBMN["run_Dereplicator"] <- "1" # "0" represent don't run and "1" represents run
```


##### Submit FBMN
```{r eval=FALSE}
source(paste0(path_utils_annotation, "/GNPS_upload_submitjobs.R"))
```

     
      
#### Dereplicator plus ðŸ•µ
##### Generate parameters ðŸ•µ
```{r eval=FALSE}
parameters_FBMN_Dereplicator_plus <- list()
parameters_FBMN_Dereplicator_plus["precursor_ion_mass_tolerance"] <- "0.02"
parameters_FBMN_Dereplicator_plus["fragment_ion_mass_tolerance"] <- "0.02"
parameters_FBMN_Dereplicator_plus["max_charge"] <- "2" # other options are 1 and 3
parameters_FBMN_Dereplicator_plus["min_score"] <- "12"
```


##### Submit Dereplicator plus
```{r eval=FALSE}
source(paste0(path_utils_annotation, "/GNPS_upload_submitjobs.R"))
```
     
  
    

#### NAP ðŸ•µ
<font color = "red">\*parameters are different from different polarities</font>
##### Generate parameters ðŸ•µ
```{r eval=FALSE}
parameters_FBMN_NAP <- list()
parameters_FBMN_NAP["number_of_a_cluster_index"] <- "0"
parameters_FBMN_NAP["cosine_value_to_subselect_inside_a_cluster"] <- "0.7" 
parameters_FBMN_NAP["n_first_candidates_for_consensus_score"] <- "10"
parameters_FBMN_NAP["use_fusion_result_for_consensus"] <- "on" # if deselect, ""
parameters_FBMN_NAP["accuracy_for_exact_mass_candidate_search_ppm"] <- "15"
parameters_FBMN_NAP["structure_database"] <- "GNPS,HMDB,SUPNAT,NPAtlas,CHEBI,DRUGBANK,FooDB" 
parameters_FBMN_NAP["maximum_number_of_candidate_structures_in_the_graph"] <- "10"
```

     
<font color = "red">Be careful the inputs of parameters depending on the polarity, so only change the inputs related to the polarity you are working on</font>
```{r eval=FALSE}
if (polarity == "POS") {
  
  parameters_FBMN_NAP["acquisition_mode"] <- "Positive"
  parameters_FBMN_NAP["adduct_ion_type"] <- "[M+H]" # other options are "[M]", "[M+NH4]", "[M+Na]", "[M+K]", "[M+ACN+H]" 
  parameters_FBMN_NAP["multiple_adduct_types"] <- "[M+Na]" 

} else if (polarity == "NEG") {
  
  parameters_FBMN_NAP["acquisition_mode"] <- "Negative" 
  parameters_FBMN_NAP["adduct_ion_type"] <- "[M-H]" # other options are "[M+Cl]", "[M+FA-H]"
  parameters_FBMN_NAP["multiple_adduct_types"] <- "[M+Cl]"
                
}  
```


##### Submit NAP
```{r eval=FALSE}
source(paste0(path_utils_annotation, "/GNPS_upload_submitjobs.R"))
```

     



#### (Optional) MS2LDA âœˆï¸ 
<font color = "red">It is only available when you preprocessed MS2 by MZmine</font> 
##### Generate parameters ðŸ•µ
```{r eval=FALSE}
parameters_FBMN_MS2LDA <- list()
parameters_FBMN_MS2LDA["bin_width"] <- "0.01" #other options are 0.005, 0.05, 0.1, 0.5
parameters_FBMN_MS2LDA["number_of_lda_iterations"] <- "1000"
parameters_FBMN_MS2LDA["minimum_ms2_intensity"] <- "100"
parameters_FBMN_MS2LDA["lda_free_motifs"] <- "200"
parameters_FBMN_MS2LDA["gnps_motif_inclusion"] <- "yes" #if deselect, "no"
parameters_FBMN_MS2LDA["massbank_motif_inclusion"] <- "yes"
parameters_FBMN_MS2LDA["urine_motif_inclusion"] <- "yes" 
parameters_FBMN_MS2LDA["euphorbia_motif_inclusion"] <- "no"
parameters_FBMN_MS2LDA["rhamnaceae_plant_motif_inclusion"] <- "no"
parameters_FBMN_MS2LDA["streptomyces_and_salinisporus_motif_inclusion"] <- "no"
parameters_FBMN_MS2LDA["photorhabdus_and_xenorhabdus_motif_inclusion"] <- "no" 
parameters_FBMN_MS2LDA["user_motif_inclusion"] <- "None" 
parameters_FBMN_MS2LDA["overlap_score_threshold"] <- "0.3"
parameters_FBMN_MS2LDA["probability_value_threshold"] <- "0.1"
parameters_FBMN_MS2LDA["topx_in_node"] <- "5" 
```


##### Submit MS2LDA 
```{r eval=FALSE}
source(paste0(path_utils_annotation, "/GNPS_upload_submitjobs.R"))
```



  
  
#### MNE (molnetenhancer) ðŸ•µ
##### Generate parameters ðŸ•µ  
```{r eval=FALSE}
parameters_FBMN_MNE <- list()
parameters_FBMN_MNE["enter_varquest_id"] <- "None"    # leave it as "None" if this id is not available 

    #If ids are not available, please provide them
parameters_FBMN_MNE["enter_nap_id"] <- FBMN_NAP_task_id
parameters_FBMN_MNE["enter_gnps_task_id"] <- FBMN_task_id
```

<font color = "red">If you preprocess your MS2 data by using MZmine, replace the value below with id of job MS2LDA</font>
```{r eval=FALSE}
parameters_FBMN_MNE["enter_ms2lda_job_id"] <- "None"
```
   
   

##### Submit MNE
```{r eval=FALSE}
source(paste0(path_utils_annotation, "/GNPS_upload_submitjobs.R"))
```




 

















### GNPS-Download results of jobs you have run ðŸ•µ
#### Source paths on the server ðŸ•µ
```{r eval=FALSE}
source("H:/From_SUND/Scripts/utils/utils_MS2_set_up/set_up_paths.R")
```
 


#### Provide polarity (upper case) ðŸ•µ
```{r eval=FALSE}
polarity <- "NEG"
```



#### Provide the path of storing downloaded files ðŸ•µ
```{r eval=FALSE}
download_path <- "H:/From_SUND/Scripts/outputs"
```
   


#### Provide project information ðŸ•µ
```{r eval=FALSE}
project_name <- ""
round <- ""
sample_type <- ""
omics <- ""
method <- ""
```

   

#### Provide the absolute path of "list of job ids" by including the name of that list ðŸ•µ
<font color = "red">name should start with **jobid**</font>
```{r eval=FALSE}
path_list <- "H:/From_SUND/Scripts/outputs/jobids_FBMN_workflow_test_1_serum_metabolomics_RP_POS.rds"
list_jobid <- readRDS(path_list)
```

 

#### Download results from the list of job ids
```{r eval=FALSE}
source(paste0(path_utils_annotation, "/GNPS_downloadjobs.R"))
```
   
      
      
      