# Small tools
This chapter consists of: 

1. Among compound name, if you have any one as identifier (PubChem id (cid), KEEG id, HMDB, CAS), you will get the rest of them and corresponding chemical properties related to this compound


<font color = "red">Copy excel file under the folder of **utils_DBs_api**, replace the context of identifier as yours. e.g. If your identifier is PubChem_CID, choose the sheet name as PubChem_CID, replace the context of PubChem_CID numbers as yours</font>




## Play with various ids
The script `DBs_ids_properties.R` is available under the folder of `J:\CBMR\SUN-CBMR-Metabolomics\Workflow\Script\modules`


### Source paths on the server
```{r eval=FALSE}
source("H:/From_SUND/Scripts/utils/utils_MS2_set_up/set_up_paths.R")
```



### Provide identifier for grabbing other information 🕵
<font color = "red">You have to choose one from these 5 options **("PubChem_CID", "Compound_Name", "KEGG", "CAS", "HMDB")**</font>
```{r eval=FALSE}
identifier <- "PubChem_CID" 
```



### Provide filename and sheetname for searching other information 🕵
absolute path
```{r eval=FALSE}
filename_xlsx <- "H:/From_SUND/Scripts/test/test_DB_ids.xlsx"
```



### What properties you would like to get 🕵
You could find other options from function `get_info_based_cid_to_xlsx.R` under the folder of containing functions
```{r eval=FALSE}
properties <- c("IUPACName", "InChIKey", "CanonicalSMILES", "MonoisotopicMass")
```


### Provide the path for containing output 🕵
```{r eval=FALSE}
path_output <- "H:/From_SUND/Scripts/outputs"
```


### Conduct 
```{r eval=FALSE}
source(paste0(path_utils_DBs_api, "/DBs_api.R"))

```





      